data-collection

### 2019-03-21 data-collection.Rmd
made more concise

Raw data is sourced online from the .csv and .xlsx files from the AEC and ABS websites. The format of these files change over the years, meaning that significant effort is required to extract the appropriate electoral information. All data wrangling is done using `R`, predominantly using the tools from the `dplyr` [@dplyr] and `readxl` [@readxl] packages, providing fast consistent tools for data manipulation and functions to import .xlsx files (respectively).

The 2001 and 2006 Census data is published in a format where each electorate has a separate document, making it difficult to use the `dplyr` tools. Instead, cells had to be selected from each individual file to construct the desired variables. For 2011 and 2016, the available Census data packs contain a separate document for each question and are easily compatible with the `dplyr` verbs, as are the published election vote outcomes.

This work is entirely reproducible, and all scripts can be found in the github repository for the `eechidna` `R` package. These scripts also provide a resource to help wrangle data for future Censuses and elections.

>>>>

Raw data is sourced online from the AEC and ABS websites in .csv and .xlsx files. The format of these files change over the years, making extracting the appropriate information a big task. The functions available in the `dplyr` [@dplyr] and `readxl` [@readxl] `R` packages are very useful, as they provide fast consistent tools for data manipulation and functions to import .xlsx files (respectively). The 2001 and 2006 Census data are however published in a format where each electorate has a separate document, making it difficult to use the `dplyr` tools and instead cells have to be selected from each individual file to construct the desired variables. All scripts required for the data wrangling process can be found in the github repository for the `eechidna` `R` package, along with the raw data. The `eechidna` package makes this study is entirely reproducible and also provides a resource to help wrangle data for future Censuses and elections, when they become available.
